\documentclass[pdf]
{beamer}
\mode<presentation>{}

\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{calc}                   
   

\newcommand\bayeseq{\mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily Bayes}}}{=}}}

\title{Prediction of RNA and DNA binding sites: weekly report}
\subtitle{}
\author[shortname]{Pandu Raharja \inst{1, 2} \and Julian Schmidt \inst{1, 2}}
\institute[shortinst]{\inst{1} Technische Universit\"at M\"unchen \and %
                      \inst{2} Ludwig-Maximilians-Universit\"at M\"unchen}

\begin{document}

%% title frame
\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Outline}
	\begin{itemize}
		\item What we did:
		\begin{itemize}
			\item Julian: xRNA binding prediction
			\item Pandu: xRNA binding site prediction
		\end{itemize}
		\item Problems.  
	\end{itemize}
\end{frame}

\begin{frame}{As always:}
	\begin{itemize}
		\item Scripts and results could be found in:
		\href{https://github.com/raharjaliu/BIFers}{https://github.com/raharjaliu/BIFers}
	\end{itemize}
\end{frame}

\begin{frame}
	\begin{center}
		\Large Part I: xRNA binding prediction
	\end{center}
\end{frame}

\begin{frame}
	\begin{center}
		\Large Part II: xRNA binding site prediction
	\end{center}
\end{frame}

%\begin{frame}{Project Specification}
%	\begin{itemize}
%		\item Java is for enterprise solution.
%		\item Development in Python $\rightarrow$ jupyter, scipy, scikit-learn, (Theano, TensorFlow, CNTK et al. if ever needed)
%	\end{itemize}
%\end{frame}

\begin{frame}{Intro}
	\begin{itemize}
		\item We're a bit late onto the game due to illness and conference.
		\item Extracted features could be found in \texttt{/mnt/project/pp2\_1516/xrna\_raharjaschmidt/} \texttt{machine\_learning/\{dna\_big.arff,rna\_big.arff\}}.
	\end{itemize}
\end{frame}

\begin{frame}{Extraction of Features on ppDNA2}
	\begin{itemize}
		\item \texttt{query.disis not found.}
		\item \texttt{Q84ZU4: no significant pfam hit, using default values...}
		\item \texttt{P03206} \textbf{(same warning)}
	\end{itemize}
\end{frame}

\begin{frame}{Extraction of Features on ppRNA2}
	\begin{itemize}
		\item \texttt{query.disis not found.}
		\item \texttt{Processing P17574... ParseError: "It seems that we have a situation now. The expected amount of columns is 22, found: \%s!" \% len(tokens)}\\
		\item \texttt{P24264} \textbf{(same ParseError)}
		\item \texttt{P67876: no significant pfam hit, using default values...}
		\item \texttt{P0C206} \textbf{(same warning)}
		\item \texttt{P0C8P8} \textbf{(same warning)}
		\item \texttt{P07243} \textbf{(same warning)}
		\item \texttt{Q57817} \textbf{(same warning)}
		\item \texttt{P04891} \textbf{(same warning)}
		\item \texttt{P18683} \textbf{(same warning)}
	\end{itemize}
\end{frame}

\begin{frame}{Machine Learning Sorcery}
	Some considerations:
	\begin{itemize}
		\item Stack choice: not a big fan of Java but features are contained in ARFF already:\\
			$\rightarrow$ Weka binding of Python?
		\item Easy model (SVN, DT/RF etc) vs. sophisticated model (deep representation learning and all the new fancy things coming out of NIPS/ICML 201X):\\
		$\rightarrow$ Implementation \textbf{will} be constrained by Weka (and time).
		
		\item Single model vs. ensemble learning (with boosting etc).
		\item Time constraint: exams and works.
	\end{itemize}
\end{frame}

\begin{frame}{Some notes regarding Weka on Py}
	\begin{itemize}
		\item Seems to be possible: \href{http://www.cs.waikato.ac.nz/~eibe/WEKA_Ecosystem.pdf}{http://www.cs.waikato.ac.nz/\textasciitilde eibe/WEKA\_Ecosystem.pdf}
		\item Requires python-weka-wrapper and cos's:\\
		\texttt{\$sudo apt-get install python-pip python-numpy python-dev python-imaging python-matplotlib \textbf{python-pygraphviz} \textbf{imagemagick}} \\
		\texttt{\$sudo pip install \textbf{javabridge} \textbf{python-weka-wrapper}}\\
		$\rightarrow$ are all these installed on the server?
		\item Actually  requires \textbf{starting-up of JVM on Python}.
	\end{itemize}
\end{frame}

\begin{frame}{Example (1)}
	\begin{itemize}
		\item Starting the JVM from Python:\\
			\texttt{import weka.core.jvm as jvm}
			\texttt{jvm.start()}
		\item Getting help:\\
			help(jvm.start)
		\item Loading and printing some data in ARFF format:\\
			\texttt{from weka.core.converters import Loader}\\
			\texttt{l = Loader("weka.core.converters.ArffLoader")}\\
			\texttt{d = l.load\_file("weka-3-7-11/data/iris.arff")}\\
			\texttt{d.set\_class\_index(d.num\_attributes() - 1)}\\
			\texttt{print(d)}
	\end{itemize}
\end{frame}

\begin{frame}{Example (2)}
	\begin{itemize}
		\item Building and printing a decision tree:\\
			\texttt{from weka.classifiers import Classifier}\\
			\texttt{c = Classifier("weka.classifiers.trees.J48")}\\
			\texttt{c.build\_classifier(d)}\\
			\texttt{print(c)}
		\item Evaluating classifier using cross-validation:\\
			\texttt{from weka.classifiers import Evaluation}\\
			\texttt{from weka.core.classes import Random}\\
			\texttt{e = Evaluation(d)}\\
			\texttt{e.crossvalidate\_model(c, d, 10, Random(1))}\\
			\texttt{print(e.percent\_correct())}\\
			\texttt{print(e.to\_summary())}\\
			\texttt{print(e.to\_class\_details())}
	\end{itemize}
\end{frame}

\begin{frame}{Some notes regarding prediction}
	\begin{itemize}
		\item What constitutes a good predictor?\\
		\begin{itemize}
			\item which scoring function to optimize?\\
			$\rightarrow$ $F_\beta$, recall, coverage?
		\end{itemize}
		\item Relaxed or rigid definition of binding residue?\\
			\texttt{-!!!-} vs \texttt{-!-!-} vs \texttt{--!!-} vs \texttt{-!!!!}
		\item etc (what is the meaning of life?)
	\end{itemize}
\end{frame}


\begin{frame}{References}

\end{frame}


\end{document}
